Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Add miniplots
clean up 4

To answer this question, this paper presents \sys, a shell \todo{preprocessor} that transforms shell pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
The key insight behind \sys is that the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation
% FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
\sys builds on this insight with a careful study of the distributability properties of shell primitives and commands, a pipeline rewriting pass that identifies \todo{maximal} sub-expressions as candidates for scale-out, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
A \sys-enabled $p_1$ will run \ttt{tr}s in parallel streams,
  use a mostly-parallel tree of \ttt{sort}s,
  run \ttt{uniq} mostly in parallel,
  \ttt{head} in one of the streams,
  and (trivially) merge streams in \ttt{out}.

@@

The paper is structured as follows.
It first starts with a background section outlining pipeline concepts and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{recipes} highlight key contributions:
\begin{itemize}

@@

  \item
  \S\ref{ir} presents a set of rewriting transformations for identifying maximal pipeline sub-expressions, candidates for scale-out.

@@

\heading{Pure Commands}
%
Together with the commands in \sta, that are always easy to
parallelize, there also exists a subclass of commands in \pur that can
be parallelized by separating them into a map and a reduce
operation. In order to allow command developers to extend \sys with
information about how to parallelize new pure commands, \sys offers an
interface to specify how to distribute a pure command.

\TODO{I am not sure a general interface is so easy to design. It needs
  more though. It might be beneficial to just talk about sort and wc
  here and how we implemented them and nothing more. Or maybe this
  could then go to the implementation? Or maybe say that one can write
  a python function that given a node of the graph, transforms it into
  many. I am not sure what is best...}

@@

\TODO{Is the following paragraph best suited here? It describes an
  assumption that we make about commands, to guarantee the validity of
  our transformations. The assumption is needed due to the limitation
  of the programming model of one input one output per command.}

Note that nodes can read from more files than just the files of their
stream (or respectively write to more files that their output stream),
however these files are static (e.g. used for configuration or logging
\kk{Would an example here help}) and do not represent streams of data,
and therefore are not considered part of the dataflow graph. We assume
that these static files can only be accessed by one node, thus
ensuring that they do not interfere with the distributed
implementation.
%% Because of the assumption in section Front End \ref{}, that each file
%% exists only once in the dataflow graph, we can safely assume that
%% reading and writing to these static files does not interfere with the
%% distributed implementation, and doesn't alter the behaviour of the
%% program.

@@

\TODO{Show an example pipe and its graph}.

\begin{center}
\small
\begin{tikzpicture}[node distance=2.25cm, ->]
\node (S) {};
\node (A) [draw, right of=S, node distance=1.75cm] {node 1};
\node (B) [draw, right of=A] {node 2};
\node (C) [draw, right of=B] {node 3};
\node (E) [right of=C, node distance=1.75cm] {};
\path (S) edge node[above] {input} (A);
\path (A) edge node[above] {stream} (B);
\path (B) edge node[above] {stream} (C);
\path (C) edge node[above] {output} (E);
\end{tikzpicture}
\end{center}

@@

\kk{(Maybe) It might be beneficial to mention that many inputs do not
  represent the same thing as many outputs. These two notions are not
  symmetric.}

\begin{figure*}
\centering
\begin{tikzpicture}[->, >=to, auto, node distance=1cm, semithick, transform shape, inner sep=2pt]
%
\small
%
\node (M1) {};
\node (M2) [draw, right of=M1, node distance=2cm] {Map};
\node (M3) [draw, right of=M2, node distance=3cm] {GroupBy(Reduce)};
\node (M4) [right of=M3, node distance=3cm] {};
%
\path (M1) edge node {input} (M2);
\path (M2) edge node {stream} (M3);
\path (M3) edge node {output} (M4);
\end{tikzpicture}
\end{figure*}

\begin{figure*}
\newcommand{\Split}{\text{Split}}
\newcommand{\Merge}{\text{Merge}}
\newcommand{\Map}{\text{Map}}
\newcommand{\GroupBy}{\text{GroupBy}}
\newcommand{\Reduce}{\text{Reduce}}
\centering
\begin{tikzpicture}[->, >=to, auto, node distance=0.6cm, semithick, transform shape, inner sep=1.75pt]
%
\footnotesize
%
\node (M1) {};
\node (M2) [draw, right of=M1, node distance=1.3cm] {$\Split$};
\node (M3) [right of=M2, node distance=1.5cm] {};
\node (M4) [right of=M3, node distance=2.5cm] {};
\node (M5) [draw, right of=M4, node distance=2.2cm] {$\Merge$};
\node (M6) [draw, right of=M5, node distance=3.8cm] {$\GroupBy(K_2,\Reduce)$};
\node (M7) [draw, right of=M6, node distance=3cm] {$\Merge_K$};
\node (M8) [right of=M7, node distance=2cm] {};
%
\node (T3) [draw, above of=M3] {$\Map$};
\node (T4) [draw, above of=M4] {$\Split_K$};
\node (T5) [draw, above of=M5] {$\Merge$};
\node (T6) [draw, above of=M6] {$\GroupBy(K_1,\Reduce)$};
%
\node (B3) [draw, below of=M3] {$\Map$};
\node (B4) [draw, below of=M4] {$\Split_K$};
\node (B5) [draw, below of=M5] {$\Merge$};
\node (B6) [draw, below of=M6] {$\GroupBy(K_3,\Reduce)$};
%
\path (M1) edge node {$A$} (M2);
\path (M2) edge[bend left=10] node {$A$} (T3);
\path (M2) edge[bend right=10] node[swap] {$A$} (B3);
\path (M5) edge node {$K_2 \times B$} (M6);
\path (M6) edge (M7);
\path (M7) edge node {$K \times B$} (M8);
%
\path (T3) edge node {$K \times B$} (T4);
\path (T4) edge (T5);
\path (T4) edge (M5);
\path (T4.330) edge[bend right=10] (B5.170);
\path (T5) edge node {$K_1 \times B$} (T6);
\path (T6) edge[bend left=10] node {$K_1 \times B$} (M7);
%
\path (B3) edge node {$K \times B$} (B4);
\path (B4) edge (B5);
\path (B4) edge (M5);
\path (B4.30) edge[bend left=10] (T5.190);
\path (B5) edge node {$K_3 \times B$} (B6);
\path (B6) edge[bend right=10] node[swap] {$K_3 \times B$} (M7);
%
\end{tikzpicture}
\caption{Distributed implementation of the map-reduce pipeline $\Map \gg \GroupBy(K,\Reduce)$.}
\label{fig:mapReduce}
\end{figure*}

@@

As mentioned above, the dataflow graph exposes task
parallelism. Different nodes in the graph can be executed
concurrently, communicating through the edges. Task level parallelism
is already exposed by the shell, by using pipes \ttt{|} and the
background operator \ttt{\&}. Unfortunately, simple task
parallelism leaves a lot to be desired, since scaling a computation
requires manually introducing more operators.

In order to adequately utilize the available computational resources,
a distributed implementation should exploit data parallelism. Data
parallelism is based on the observation that some operations produce
the same result when performed independently on subsets of the input
data, merging the results afterwards. This is the basic optimization
that is used by popular distributed processing systems such as
MapReduce \cite{DG2004MR} and Apache Spark \cite{spark:12}. Unfortunately, the
dataflow graph model of most of these systems is not expressive enough
to represent data parallelism \km{not sure this is true}, so the distributed implementations that
they perform do not preserve the semantics of their dataflow model.

In contrast, our dataflow model inherently supports the data
parallelism that is found in shell programs. More precisely, data
parallelism can be easily exposed as task parallelism in our model. A
very important consequence of this is that we can iteratively apply
optimizations that expose data parallelism, or even revert them when
the resulting dataflow graph is too wide. This flexibility enables
unified reasoning and implementation of the unoptimized and optimized
version of the dataflow graph. \kk{This is interesting, and should be
  moved up (or rephrased in the introduction)}

Before describing the different types of parallelization
optimizations, we formalize the intuition about stateless and pure
commands that was described in \Cref{cmd}.
\nv{TODOs
  (i) highlight earlier the antithesis between the formalisms in this section and the informalities of the previous (me);
  (ii) try to add a proof \emph{sketch} pointing to these formalisms (to show their value), and we can point to the TR for the longer proof.
}
%
As mentioned there, stateless commands operate independently on
individual elements of the stream (characters, lines, or files)
without maintaining any state. Some examples include \ttt{grep},
\ttt{basename}, and \ttt{tr}. Formally, a commmand $f$ is stateless if
it is ``linear'' with respect to concatenation, i.e. the following
equation holds:

@@

\km{This is a nice characterization, which I think is true in most settings. There is a caveat though: You can have stateless programs that emit output when they start (before they consume the stream) and/or when they consume the EOF symbol. In this case I am not sure the equation above holds.}

@@

As mentioned in \Cref{ir}, in order to generate the distributed
implementation of a shell script, \ttt{Dish} first translates it to
a dataflow graph. However, there are several components in shell
programs that cannot be arbitrarily parallelized without affecting the
program behaviour, e.g. commands producing an irreversible effect, or
commands connected with a \ttt{\&\&} operator. In addition, the
fact that the shell is \todo{extremely dynamic}, further increases the
challenge of correctly identifying what parts can be distributed.

@@

In order to address this issue, we \todo{introduce} the notion of
distributable program regions, and we design a translation pass that
given the abstract syntax tree of a shell script identifies
distributable regions and translates each of them to a dataflow
graph. The AST of the shell script is produced using a POSIX compliant
parser~\cite{libdash}.

@@

Whenever the algorithm encounters a pipe node, it recursively
translates its subcomponents, and then merges them in a dataflow graph
by connecting the output of the first with the input of the second,
\etc. Before the different dataflow graphs are connected, the
algorithm checks that at most one node in the graph writes at every
file, and at most one node reads from a file that another node writes
to. This is important, in order to avoid inconsistent behaviour after
distributing nodes in the dataflow graph (i.e. by introducing to
concurrent reads and writes to the same file when
parallelizing). Whenever the algorithm encounter an \ttt{\&\&} node,
it recursively translates its subcomponents (similarly to the pipe
node), but then does not merge them in a large dataflow
graph. Finally, whenever the algorithm encounters a command, it first
checks whether it is safe to parallelize it. A command is considered
to be safe, if it does not make any modification to the shell state
(e.g. changing the current directory, modifying environment
variables), and if it does not read from any \todo{read-once} file,
like a fifo pipe. If the command is considered safe, its category is
identified and a node containing that command is created and added to
a singleton dataflow graph. If the command is considered unsafe, it is
still added to the dataflow graph, but cannot be further parallelized
by the optimizer.

@@

@@

\begin{figure*}[t]
    \centering
    %% \subcaptionbox{\label{eval:minimal_grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:minimal_sort}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:topn}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:wf}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:spell}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \caption{a}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    \caption{todo}
    \label{fig:microbenchmarks}
\end{figure*}

>>>>

To answer this question, this paper presents \sys, a shell \todo{preprocessor} that transforms shell pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
The key insight behind \sys is that a large part of the shell language can be encoded using a dataflow graph model, providing structure to distribute computations.
%% \kk{Replaced that: the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation. }
% FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
\sys builds on this insight with a careful study of the distributability properties of shell primitives and commands, a definition of a dataflow graph model that is suitable for the shell, a set of parallelization optimizations that preserve the behaviour of the graph, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
A \sys-enabled $p_1$ will run \ttt{tr}s in parallel streams,
  use a mostly-parallel tree of \ttt{sort}s,
  run \ttt{uniq} mostly in parallel,
  \ttt{head} in one of the streams,
  and (trivially) merge streams in \ttt{out}.

@@

The paper is structured as follows.  It first starts with a background
section outlining pipeline concepts and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{recipes} highlight key
contributions: \TODO{Change the 1st and the 3rd to reflect the new
  section layout. I already changed the second.}
\begin{itemize}

@@

  \item
  \S\ref{ir} presents a dataflow graph model that can encode shell programs, and a set of parallelization transformations that preserve its semantics.

@@

%% \heading{Pure Commands}
%
\noindent
Together with the commands in \sta, that are always easy to
parallelize, there also exists a subclass of commands in \pur that can
be parallelized by separating them into a map and a reduce
operation. In order to allow command developers to extend \sys with
information about how to parallelize new pure commands, \sys offers a
programmatic interface to specify how to distribute a pure command.

\tr{I am not sure a general interface is so easy to design. It needs
  more though. It might be beneficial to just talk about sort and wc
  here and how we implemented them and nothing more. Or maybe this
  could then go to the implementation? Or maybe say that one can write
  a python function that given a node of the graph, transforms it into
  many. I am not sure what is best...}

@@

%% \TODO{Is the following paragraph best suited here? It describes an
%%   assumption that we make about commands, to guarantee the validity of
%%   our transformations. The assumption is needed due to the limitation
%%   of the programming model of one input one output per command.}

Note that nodes can read from more files than just the files of their
stream (or respectively write to more files that their output stream),
however these files are static (e.g. used for configuration or
logging) and do not represent streams of data, and therefore are not
considered part of the dataflow graph. We assume that these static
files can only be accessed by one node, thus ensuring that they do not
interfere with the distributed implementation.
%% Because of the assumption in section Front End \ref{}, that each file
%% exists only once in the dataflow graph, we can safely assume that
%% reading and writing to these static files does not interfere with the
%% distributed implementation, and doesn't alter the behaviour of the
%% program.

@@

%% \TODO{Show an example pipe and its graph}.

%% \begin{center}
%% \small
%% \begin{tikzpicture}[node distance=2.25cm, ->]
%% \node (S) {};
%% \node (A) [draw, right of=S, node distance=1.75cm] {node 1};
%% \node (B) [draw, right of=A] {node 2};
%% \node (C) [draw, right of=B] {node 3};
%% \node (E) [right of=C, node distance=1.75cm] {};
%% \path (S) edge node[above] {input} (A);
%% \path (A) edge node[above] {stream} (B);
%% \path (B) edge node[above] {stream} (C);
%% \path (C) edge node[above] {output} (E);
%% \end{tikzpicture}
%% \end{center}

@@

%% \kk{(Maybe) It might be beneficial to mention that many inputs do not
%%   represent the same thing as many outputs. These two notions are not
%%   symmetric.}

%% \begin{figure*}
%% \centering
%% \begin{tikzpicture}[->, >=to, auto, node distance=1cm, semithick, transform shape, inner sep=2pt]
%% %
%% \small
%% %
%% \node (M1) {};
%% \node (M2) [draw, right of=M1, node distance=2cm] {Map};
%% \node (M3) [draw, right of=M2, node distance=3cm] {GroupBy(Reduce)};
%% \node (M4) [right of=M3, node distance=3cm] {};
%% %
%% \path (M1) edge node {input} (M2);
%% \path (M2) edge node {stream} (M3);
%% \path (M3) edge node {output} (M4);
%% \end{tikzpicture}
%% \end{figure*}

%% \begin{figure*}
%% \newcommand{\Split}{\text{Split}}
%% \newcommand{\Merge}{\text{Merge}}
%% \newcommand{\Map}{\text{Map}}
%% \newcommand{\GroupBy}{\text{GroupBy}}
%% \newcommand{\Reduce}{\text{Reduce}}
%% \centering
%% \begin{tikzpicture}[->, >=to, auto, node distance=0.6cm, semithick, transform shape, inner sep=1.75pt]
%% %
%% \footnotesize
%% %
%% \node (M1) {};
%% \node (M2) [draw, right of=M1, node distance=1.3cm] {$\Split$};
%% \node (M3) [right of=M2, node distance=1.5cm] {};
%% \node (M4) [right of=M3, node distance=2.5cm] {};
%% \node (M5) [draw, right of=M4, node distance=2.2cm] {$\Merge$};
%% \node (M6) [draw, right of=M5, node distance=3.8cm] {$\GroupBy(K_2,\Reduce)$};
%% \node (M7) [draw, right of=M6, node distance=3cm] {$\Merge_K$};
%% \node (M8) [right of=M7, node distance=2cm] {};
%% %
%% \node (T3) [draw, above of=M3] {$\Map$};
%% \node (T4) [draw, above of=M4] {$\Split_K$};
%% \node (T5) [draw, above of=M5] {$\Merge$};
%% \node (T6) [draw, above of=M6] {$\GroupBy(K_1,\Reduce)$};
%% %
%% \node (B3) [draw, below of=M3] {$\Map$};
%% \node (B4) [draw, below of=M4] {$\Split_K$};
%% \node (B5) [draw, below of=M5] {$\Merge$};
%% \node (B6) [draw, below of=M6] {$\GroupBy(K_3,\Reduce)$};
%% %
%% \path (M1) edge node {$A$} (M2);
%% \path (M2) edge[bend left=10] node {$A$} (T3);
%% \path (M2) edge[bend right=10] node[swap] {$A$} (B3);
%% \path (M5) edge node {$K_2 \times B$} (M6);
%% \path (M6) edge (M7);
%% \path (M7) edge node {$K \times B$} (M8);
%% %
%% \path (T3) edge node {$K \times B$} (T4);
%% \path (T4) edge (T5);
%% \path (T4) edge (M5);
%% \path (T4.330) edge[bend right=10] (B5.170);
%% \path (T5) edge node {$K_1 \times B$} (T6);
%% \path (T6) edge[bend left=10] node {$K_1 \times B$} (M7);
%% %
%% \path (B3) edge node {$K \times B$} (B4);
%% \path (B4) edge (B5);
%% \path (B4) edge (M5);
%% \path (B4.30) edge[bend left=10] (T5.190);
%% \path (B5) edge node {$K_3 \times B$} (B6);
%% \path (B6) edge[bend right=10] node[swap] {$K_3 \times B$} (M7);
%% %
%% \end{tikzpicture}
%% \caption{Distributed implementation of the map-reduce pipeline $\Map \gg \GroupBy(K,\Reduce)$.}
%% \label{fig:mapReduce}
%% \end{figure*}

% \begin{figure}[t]
% \centering
\includegraphics[width=0.25\textwidth]{\detokenize{./figs/dish_g1.pdf}}

\includegraphics[width=0.15\textwidth]{\detokenize{./figs/dish_g2.pdf}}
% \caption{
%   \textbf{\sys transformation overview.}
%   Given a shell pipeline, \sys leverages command distributability to identify
%   high-distributability stages, rewrite them, and orchestrate their execution.
% }
% \vspace{-15pt}
% \label{fig:overview}
% \end{figure}

@@

As mentioned above, the dataflow graph exposes task
parallelism. Different nodes in the graph can be executed
concurrently, communicating through the edges.
%% Task level parallelism is already exposed by the shell, by using
%% pipes \ttt{|} and the background operator \ttt{\&}.
Unfortunately, simple task parallelism leaves a lot to be desired,
since scaling a computation requires manually introducing more
operators.

In order to adequately utilize the available computational resources,
a distributed implementation should exploit data parallelism. Data
parallelism is based on the observation that some operations produce
the same result when performed independently on subsets of the input
data, merging the results afterwards. Exploiting data parallelism is
one of the major reasons that popular distributed stream processing
systems (such as MapReduce \cite{DG2004MR} and Apache Spark
\cite{spark:12}) achieve significant performance. Unfortunately, the
optimizations in many of these systems do not preserve the dataflow
model semantics, blurring the lines between specification,
optimization, and implementation.

In contrast, our dataflow model inherently supports the data
parallelism that is found in shell programs. More precisely, data
parallelism can be easily exposed as task parallelism in our model. A
very important consequence of this is that we can iteratively apply
optimizations that expose data parallelism, or even revert them when
the resulting dataflow graph is too wide. This flexibility unifies the
unoptimized and optimized versions of a computation, enabling thinking
about them with the same conceptual tools.

Before describing the different types of parallelization
optimizations, we formalize the intuition about stateless and pure
commands that was described in \Cref{cmd}.
\nv{TODOs
  (i) highlight earlier the antithesis between the formalisms in this section and the informalities of the previous (me)
}
%
As mentioned there, stateless commands operate independently on
individual elements of the stream (characters, lines, or files)
without maintaining any state. Some examples include \ttt{grep},
\ttt{basename}, and \ttt{tr}. Formally, a commmand $f$ is stateless if
it is ``linear'' with respect to concatenation, i.e. the following
equation holds:

@@

\tr{This is a nice characterization, which I think is true in most
  settings. There is a caveat though: You can have stateless programs
  that emit output when they start (before they consume the stream)
  and/or when they consume the EOF symbol. In this case I am not sure
  the equation above holds.}

@@

As mentioned in \Cref{ir}, in order to generate the distributed
implementation of a shell script, \ttt{Dish} first translates it to
a dataflow graph. However, there are several components in shell
programs that cannot be arbitrarily parallelized without affecting the
program behaviour, e.g. commands producing an irreversible effect, or
commands connected with a \ttt{\&\&} operator. In addition, the
fact that the shell is highly dynamic, further increases the
challenge of correctly identifying what parts can be distributed.

@@

In order to address this issue, we introduce the notion of
distributable program regions, and we design a translation pass that
given the abstract syntax tree of a shell script identifies
distributable regions and translates each of them to a dataflow
graph. The AST of the shell script is produced using a POSIX compliant
parser~\cite{libdash}.

@@

Whenever the algorithm encounters a pipe node, it recursively
translates its subcomponents, and then merges them in a dataflow graph
by connecting the output of the first with the input of the second,
\etc. Before the different dataflow graphs are connected, the
algorithm checks that at most one node in the graph writes at every
file, and at most one node reads from a file that another node writes
to. This is important, in order to avoid inconsistent behaviour after
distributing nodes in the dataflow graph (i.e. by introducing to
concurrent reads and writes to the same file when
parallelizing). Whenever the algorithm encounter an \ttt{\&\&} node,
it recursively translates its subcomponents (similarly to the pipe
node), but then does not merge them in a large dataflow
graph. Finally, whenever the algorithm encounters a command, it first
checks whether it is safe to parallelize it. A command is considered
to be safe, if it does not make any modification to the shell state
(e.g. changing the current directory, modifying environment
variables), and if it does not read from any read-once file
(e.g. pipe). If the command is considered safe, its category is
identified and a node containing that command is created and added to
a singleton dataflow graph. If the command is considered unsafe, it is
still added to the dataflow graph, but cannot be further parallelized
by the optimizer.

@@

\kk{Mention sort, wc}

@@

\begin{figure*}[t]
    \centering
    %% \subcaptionbox{\label{eval:minimal_grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:grep}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/grep_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:minimal_sort}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:topn}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:wf}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
    %% }
    %% \subcaptionbox{\label{eval:spell}}{
    %%     \includegraphics[width=0.32\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
    %% }
    %% \caption{a}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_grep_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/spell_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:grep}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/minimal_sort_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:minimal_sort}
    \end{subfigure}%

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    \caption{todo}
    \label{fig:microbenchmarks}
\end{figure*}
